---
title: Project Title
author: ""
format: pdf
execute:
  echo: true
fontsize: 11pt
geometry: margin=1in
linestretch: 1.5
---

Student Name (Student ID),

Student Name (Student ID),

Student Name (Student ID),

Student Name (Student ID)

\newpage

## Step 1:

Follow the instructions to download and load the `mfeat-mor` dataset from the UCI Machine Learning Repository.

## Step 2:

Provided code.

## Step 3:

```{r}
#Exploratory analysis code:
```

Interpretation (you can choose the tables and figures to present):

-   Statement 1
-   Statement 2
-   Statement 3
-   Statement 4

## Step 4:

Problem chosen:

Rationale:

## Step 5:

Method 1:

```{r}
#method 1 analysis
```

Why chosen method 1:

Method 2:

```{r}
#method 2 analysis
```

Why chosen method 2:

## Step 6:

Interpretation of results from Method 1 (you can choose the tables and figures to present):

-   interpretation 1
-   interpretation 2

Interpretation of results from Method 2 (you can choose the tables and figures to present):

-   interpretation 1
-   interpretation 2

Comparison of methods:

-   statement 1
-   statement 2
-   statement 3
-   statement 4
